---
title: "Exam 1"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(lubridate)
```

## Import Data

For this exam you will need to import two datasets: sleep.csv: This dataset contains data from a sleep study that looked at reaction times for control and sleep deprived individuals over the course of 10 days.

spotify_songs.csv: This dataset contains variables (columns) about songs (rows) found in the spotify library in 2019.

```{r import data}




```

# Section 1: Sleep Study

## Question 1 - Does Sleep Deprivation Impact Reaction Time?

Write the code required to create this visualization

```{r Question 1}

```

## Question 2 - When Do the Effects of Sleep Deprivation Occur?

Describe a visualization (similar to question 1) that would answer the question: What day does the mean reaction time extend beyond 300 ms for the deprived group? (***Bonus 1 pt*** - write the code required to create the visualization)

```{r Question 2}





```

# Section 2: Spotify Songs

## Question 3 - R Code in Your Own Words

Describe (in complete sentences and using the terminology we’ve used in class) what the code below does?

```{r Question 3}
spotify_songs%>%
  filter(year == 2019 & track_popularity>90)%>%
  select(year, track_popularity, track_name, track_artist, playlist_genre, key)%>%
  group_by(playlist_genre)%>%
  summarise(count = n())%>%
  ggplot(aes(x = fct_reorder(playlist_genre, count), fill = playlist_genre, y = count))+
  geom_col()+
  coord_flip()+
  guides(fill = "none")+
  labs(y = "Number of Songs with Popularity > 90 in Spotify",
       x = "Music Genre",
       title = "Number of Popular Songs from 2019")
```

## Question 4 - Exploring Acousticness in EDM and Rock Songs

Part 1: Write the code required to describe the relationship between the mean acousticness of songs and year in the edm and rock genre. 

Part 2: Using complete sentences, how has acousticness changed over the years for edm and rock songs? 






```{r Question 4}
#part 1




```

## Question 5 - Are songs getting shorter? 

Part 1: Write the code required to answer the question: Since 2010, are songs getting shorter?

Part 2: In general, are songs from specific playlist_genres getting shorter over time? Write the code required to describe the role playlist_genre has on song duration since 2010. 
```{r Question 5}
#part 1





#part 2




```

## Question 6 - Write your own exploratory data analysis question

Write an exploratory data analysis question that explores the relationships between the variables popularity, year, and track_artist. 






## Question 7 - Write the code

Write the code required to answer the question you've poised in question 6. 
```{r Question 7}





```






