---
title: "Explore the Built-in Datasets"
format: html
editor: visual
---

# Part 1

## Built-in datasets

The R language comes with numerous built-in datasets which are normally used as demo data for playing with R functions. In this activity, you will access and briefly explore one of R's built-in dataset.

## Viewing the datasets

Call the `data` function from RStudio to view all built-in datasets.

```{r}
data()
```

## Selecting a dataset and viewing contents

Find 3 datasets from that list and view the first few rows of the data (use the head() function)

```{r}
head(AirPassengers)
head(women)
head(Nile)
```

## Explore the dataset with the functions we learned in r-basics

Select the dataset you are most interested in and assign the object to a new object called "fav_data". Use the exploratory functions we've learned in class to further explore your dataset. Comment on what each function does.

```{r}
data()
rm(Nile)
precip
fav_data <- precip

summary(precip)
```

# Part 2

## Sketch your visualization based on your dataset of choice

Take the dataset that you've chosen from the built-in choices and think about what might make an interesting story / exploration. Think about the grammar of graphics, particularly the way we've talked about mapping variables to aesthetics and the creation of geometric objects.

What variables would you like to map?

What aesthetics and geometric objects would best highlight the story you want to tell?

Sketch out your visualization
