---
title: "Data Transformation Activity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Babynames Assignment

```{r}
library(tidyverse)
#install.packages("babynames")
library(babynames)
```

### 1. Look at the data (1 pt)

The package babynames contains an object of the same name that contains all the data about babynames.The babynames dataset has historical information about births of babies in the U.S.

View and examine the data and its structure to understand what variables are contained within the data

```{r}
head(babynames)
str(babynames)
```

### 2. Visually Explore the Data for Popular Girl Names (1 pt)

Filter the data for the names Emily, Kathleen, Alexandra, and Beverly.

```{r}
dat <- babynames %>% 
  filter(name %in% c("Emily","Kathleen","Alexandra","Beverly"), sex=="F")
```

Visualize the resulting data in a line graph by mapping year to the x-axis, proportion of name (prop) to the y-axis and name to color.

```{r}
ggplot(data = dat,aes(x = year,y = prop, colour=name))+
  geom_line()  
```

Because in most countries assigned sex at birth is binary, there is no data on intersex, trans or non-binary names. In lieu of that, here's the [Wikipedia page about gender-neutral names and naming laws](https://en.wikipedia.org/wiki/Unisex_name) around the world which will hopefully make you question why on earth we ascribe someone's entire gender identity to a bunch of sounds and letters we use to label them.

### 3. Create a new variable for decade (2 pts)

Create a new column for decade Hint: formula to find decade: **floor(year/10)\*10**

```{r}
new_dat <- mutate(.data = babynames, # the tibble you want to add a column to
                  decade = floor(year/10) *10) # new column name = what you want it to contain
head(new_dat)
```

### 4. Create a new dataframe that determines the mean proportion for each name by sex and decade. (2 pts)

For this I want you to explore the group_by() and summarize() functions.

```{r}
new_dat2 <- new_dat%>%
  group_by(name,sex,decade)%>%
  summarise(mean_prop = mean(prop))
```

### 5. Using your dataset from step 4, figure out the 5 most popular baby names for both sexes in the 1880 decade

```{r}
dat_1880 <- new_dat2 %>%
  filter(decade == 1880)%>%
  arrange(desc(mean_prop))

#m: John, William, James, George, Charles
#f: Mary, Anna, Emma, Elizabeth, Minnie

```

### 6. Using your dataset from step 4, create a visualization that tracks the popularity of the 5 most popular baby names in 1880 across the decades (4 pts)

```{r}
names <- c("John", "William", "James", "George", "Charles","Mary", "Anna", "Emma", "Elizabeth", "Minnie")

viz <- new_dat2 %>%
  filter(name %in% names)%>%
  ggplot(mapping = aes(x = decade, y = mean_prop, color = name))+
  geom_line()+
  facet_wrap(~sex)

viz
```
