---
title: "Data Transformation Activity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Gapminder Transformation

Load the gapminder data into a dataframe called df

```{r}
library(gapminder)
library(tidyverse)

```

Transform the data to find the mean life expectancy and total population for each continent at each year in the data. 

```{r}
df <- gapminder

df_trans <- df%>%
  group_by(continent, year)%>%
  summarise(mean_life = mean(lifeExp),
            total_pop = sum(pop))
```

Create a new variable called pop_exp that is the ratio of total population by mean life expectancy
```{r}
df_trans <- df_trans%>%
  mutate(ratio = total_pop/mean_life)
```


Filter for years after 1970 and continents Asia and Europe then sort the data by year

```{r}
continents <- c("Asia","Europe")

df_trans <- df_trans%>%
  filter(year > 1970 & continent %in% continents)%>%
  arrange(desc(year))
```

Visualize how the ratio of population and life expectancy change over time for Asia and Europe
```{r}
ggplot(df_trans, aes(x = year, y = mean_life, size = total_pop))+
  geom_point()
```

