---
title: "Babynames Continued"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

### Set up Code

Load the tidyverse and babynames packages

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(babynames)
```

### Top 5 Names from your Birth Year

Find the top names from your birth year Find the top five (boy or girl) names from your birth year and assign the output to a new object. Hint (you can use the slice(1:5) function to 'cut off' the top 5 rows of a dataset)

```{r}
#assign babynames to object
baby_names <- babynames
#group by year
baby_names_year <- baby_names%>%
  group_by(year)%>%
  #filter by birth year
  filter(year == "2002",sex == "F")%>%
  #arranges names
  arrange(desc(prop))%>%
  slice(1:5)

top5_rv2 <- baby_names_year$name
top5 <- c("Emily","Madison","Hannah","Emma","Alexis")
```

### Top 5 Names (and your own) Across the Years

Visualize the popularity of those names (and yours) across all of the years Now I want you to look at the popularity of those names (*as well as your name*) across all of the years in the dataset. This requires a strong working knowledge of the filter() function.

```{r}
baby_names%>%
  filter(name %in% c("Emily","Madison","Hannah","Emma","Alexis","Payton")&sex == "F")%>%
  ggplot(aes(year, prop, color = name))+
  geom_line()
```
